InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-25 paper.tex
Add section about LLAMA 2

>>>>

The \textbf{Llama 2} model built and released by Meta. It is available in different sizes, ranging from 7 billion to 70 billion parameters and different appliances like LLAMA 2-Chat, which is optimized for dialogue interaction. When it was released in 2023, it outperformed state-of-the-art open source models. A main refinement compared to its predecessor LLAMA, was the focus on transparency and safety including a post-training alignment. \cite{touvron2023llama}
